Plots and tables summarizing results of Poisson simulations

### 2019-12-16 analysis/poisson.Rmd
Small edit to code in poisson.Rmd.
Implemented function create.signal.plot in poisson.functions.R.

@@

This is the function used to simulate the "Spikes" data sets at
different ranges of intensities:

```{r plot-spikes-function, fig.height=4, fig.width=8}
mu.s <- spike.f(t)
plot(t,mu.s,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
```

@@

```{r plot-angles-function, fig.height=4, fig.width=8}
mu.ang <- angles.f(t)
plot(t,mu.ang,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
```

@@

```{r plot-heavisine-function, fig.height=4, fig.width=8}
mu.hs <- heavi.f(t)
plot(t,mu.hs,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
```

>>>>

Initialize the sequence of pseudorandom numbers.

@@

This plot shows the function used to simulate the "Spikes" data sets
at the $(1/100, 3)$ intensity range, along with an example data set
(black circles):

```{r plot-spikes-function, fig.height=2.5, fig.width=8}
mu.s <- 0.01 + spike.f(t)
x    <- rpois(n,mu.s)
create.signal.plot(mu.s,x)
```

@@

```{r plot-angles-function, fig.height=2.5, fig.width=8}
mu.ang <- 0.01 + angles.f(t)
x      <- rpois(n,mu.ang)
create.signal.plot(mu.ang,x)
```

@@

```{r plot-heavisine-function, fig.height=2.5, fig.width=8}
mu.hs <- 0.01 + heavi.f(t)
x     <- rpois(n,mu.hs)
create.signal.plot(mu.hs,x)
```
